Behavior Driven Development in Haskell

### 2012-05-29 paper.tex
Add Doctest as a contribution
Add doctust as a contribution (again!)
Solution wip
Comment for @kazu

\begin{itemize}
\item
    Add support for QuickCheck properties to Doctest (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

\begin{quote}\begin{itemize}
    \item
        Haddock has markup support for interactive examples, and
        Doctest can verify them.
    \item
        But it is not possible to use properties in Haddock comments
        and automatically test them.
\end{itemize} \end{quote}

@@

\begin{quote}
    \emph{TBD}
\end{quote}

@@

>>>>

\begin{itemize}
\item
    We originally implemented Doctest, back in 2010.
\item
    Add support for QuickCheck properties to Doctest (Section
    \ref{sec:user-doc} and Section \ref{sec:doctest})

@@

@@

\begin{quote}
    TBD: sol: @kazu, can you update this?
\end{quote}

@@

\begin{quote}\begin{itemize}
    \item
        We already added markup support for interactive examples to
        Haddock, back in 2010; and Doctest can verify them.
    \item
        But it is not possible to use properties in Haddock comments
        and automatically test them.
\end{itemize} \end{quote}
